Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-22 paper.tex
wrote RP7
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{We still have to mention RP7...} \textcolor{green}{I leave that to you...}

>>>>

\textbf{(RP7)} Embedded systems are typically implemented in low- and medium-level programming languages ({\it e.g.}, ANSI-C/C++/Java). Given the availability of different programming languages for writing code for embedded systems, the provision of a unified framework able to tackle low- and high-level properties, as well as system behavior, is needed to achieve code coverage in real applications. The clang compiler~\cite{Lopes:2014:GSL:2692607} seems to offer a simple and strong approach to lead software verification to another degree of completeness so that every implementation aspect of an embedded system can be addressed and evaluated. In particular, by using the clang compiler as front-end for a software verification tool, we avoid the need to maintain a proprietary front-end (a real challenge nowadays, given that the C and C++ standards are rapidly evolving), and then focus on the main tool objective, the formal program verification. Here, we provide only operation models to tackle low- and high-level system properties via an abstract representation of the associated libraries, which conservatively approximates their semantics. The clang compiler offers an industrial quality analyzer and an application programming interface to access and traverse its internal AST, which can then be used by software verifiers to generate their IR or alternatively analyze the LLVM bitcode produced by clang.
